Avancement du stage

### 2025-06-04 presentation.qmd
Ajout de geopandas

afficher_cat = ["Journalière", "1h", "3h glissante", "6h glissante", "9h glissante", "12h glissante", "24h glissante"]
df_r2_all_max["Echelle"] = pd.Categorical(df_r2_all_max["Echelle"], categories=afficher_cat, ordered=True)
df_r2_all_max["r2_txt"] = df_r2_all_max["r²"].apply(lambda x: f"{x:.2f}".lstrip("0"))

@@

# Définir une palette manuelle cohérente
color_map = {
    "Journalière": "#1f77b4",       # Bleu (Plotly[0])
    "1h": "#ff7f0e",                # Orange (Plotly[1])
    "3h glissante": "#2ca02c",      # Vert (Plotly[2])
    "6h glissante": "#d62728",      # Rouge (Plotly[3])
    "9h glissante": "#9467bd",      # Violet (Plotly[4])
    "12h glissante": "#8c564b",     # Marron (Plotly[5])
    "24h glissante": "#e377c2",     # Rose (Plotly[6])
}

>>>>

afficher_cat = [
    f"Journalière ({year_display_min}-{year_display_max})", f"Journalière ({year_display_middle}-{year_display_max})",
    "1h", "3h glissante", "6h glissante", "9h glissante", "12h glissante", "24h glissante"
    ]

df_r2_all_max["Echelle"] = pd.Categorical(df_r2_all_max["Echelle"], categories=afficher_cat, ordered=True)
df_r2_all_max["r2_txt"] = df_r2_all_max["r²"].apply(lambda x: f"{x:.2f}".lstrip("0"))

@@

# Définir une palette manuelle cohérente
color_map = {
    f"Journalière ({year_display_min}-{year_display_max})": "#17becf",       # Bleu clair
    f"Journalière ({year_display_middle}-{year_display_max})": "#1f77b4",       # Bleu (Plotly[0])
    "1h": "#ff7f0e",                # Orange (Plotly[1])
    "3h glissante": "#2ca02c",      # Vert (Plotly[2])
    "6h glissante": "#d62728",      # Rouge (Plotly[3])
    "9h glissante": "#9467bd",      # Violet (Plotly[4])
    "12h glissante": "#8c564b",     # Marron (Plotly[5])
    "24h glissante": "#e377c2",     # Rose (Plotly[6])
}
